---
title: "Exploratory analysis of Indonesian fatality data"
author: "Hyeuk Ryu"
date: "17 August 2015"
output: pdf_document
---

1. read data

```{r}
dat <- read.csv('DATA_WALD_COR_ROUND_12_Feb_2013.csv',header=0)
names(dat) <- c("pop","fat","mmi","mmi_bin","id")
dat$rat <- dat$fat/dat$pop
```

2. data by MMI 

```{r, echo=FALSE}
aggregate(dat$rat, by=list(dat$mmi_bin), length)
boxplot(rat~mmi_bin, dat)
```

2. Divide into zero and non-zero  

```{r, echo=FALSE}
aggregate(dat$rat, by=list(dat$mmi_bin), length)
boxplot(rat~mmi_bin, dat)
```

3. fatality rate at MMI 8.5

- fitting data to lognormal distribution

```{r, echo=FALSE, fig.show='asis'}
y85 <- dat$rat[dat$mmi_bin == 8.5]
y85
# ignore zero values
library(fitdistrplus)
y85_lnorm <- fitdist(y85, "lnorm", method="mle")
plot(y85_lnorm)
```

- fitting data to gamma distribution

```{r, echo=FALSE, warning=FALSE}
y85_gamma <- fitdist(y85, "gamma", method="mle")
plot(y85_gamma)
```

- fitting data to beta distribution
```{r, echo=FALSE, warning=FALSE}
y85_beta <- fitdist(y85, "beta", method="mle")
dev.new()
plot(y85_beta)
```

- compare fitted distributions

```{r}
qqcomp(list(y85_lnorm, y85_gamma, y85_beta), legendtext=c("lognormal", "gamma", "beta"))
```

4. fatality rat at MMI 8 and 8.5

```{r, echo=FALSE}
y8 <- dat$rat[dat$mmi_bin == 8.0]
y8t <- y8[y8>0.0]
```

- fitting data to lognormal distribution

```{r, echo=FALSE}
y8_lnorm <- fitdist(y8t, "lnorm", method="mle")
plot(y8_lnorm)
```

- fitting data to gamma distribution

```{r, echo=FALSE, warning=FALSE}
y8_gamma <- fitdist(y8t, "gamma", method="mle")
plot(y8_gamma)
```

- fitting data to beta distribution

```{r, echo=FALSE, warning=FALSE}
y8_beta <- fitdist(y8t, "beta", method="mle")
plot(y8_beta)
```

- compare fitted distributions

```{r}
qqcomp(list(y8_lnorm, y8_gamma, y8_beta), legendtext=c("lognormal", "gamma", "beta"))
#ks.test(y85, "plnorm", y85_lnorm$estimate)
```

5. log(rat) vs. mmi_bin

```{r}
plot(mmi_bin, log(rat))